NewAnalysis

### 2024-10-30 Code/NewAnalysis.Rmd
DQ analysis is at the bottom

```{r}
dash_and_hurdles <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  mutate(RxnTime = ifelse(RxnTime < 0.1, 0.1, RxnTime))

@@

Now we will see how the inclusion of the pooled data will influence the results
```{r}
sim_three_effect_time <- function(model, base, RxnTime) {
  simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    sd_Venue <- vc$sdcor[1]
    sd_Venue_heat <- vc$sdcor[2]
    sd_event <- vc$sdcor[3]

    z1 <- rnorm(n, sd = sd_Venue)
    z2 <- rnorm(n, sd = sd_Venue_heat)
    z3 <- rnorm(n, sd = sd_event)
    shape <- 1 / sigma(model)^2
    mu <- exp(fixef(model) + z1 + z2 + z3)

  sbase <- summary(base)
  x <- simfit(model)
  print(mean(x < RxnTime))
  #print(quantile(x, prob = c(0.00001, 0.0001, 0.0005, 0.001)))
  ## compare with and without random effect
  plot(density(x))  # with random effects
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.25, add = TRUE, col = "blue")
}
```

@@

```{r}
all_events <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles" | Event == "200 Dash") |>
  mutate(RxnTime = ifelse(RxnTime < 0.1, 0.1, RxnTime))
```

@@

>>>>

```{r}
dash_and_hurdles <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS" & Time != "DQ" & Time != "D") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles")

@@

@@

```{r}
all_events <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS" & Time != "DQ") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles" | Event == "200 Dash") |>
  mutate(RxnTime = ifelse(RxnTime < 0.1, 0.1, RxnTime))
```

@@

Based on the above evidence it seems reasonable to conclude that it is appropriate
to pool the men's 110 meter hurdles with the 100 meter dash and pool the women's
100 meter hurdles with the 100 dash but based on previous studies we are going
to separate men's and women's data.

## Testing Whether or not to include disqualfications
```{r}
dash_and_hurdles <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS" & Time != "DQ" & Time != "D") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles")
```

```{r}
cat("The number of entries of the men's 100 meter dash and 110 meter hurdles
    without disqualifcations is", nrow(dash_and_hurdles))
```

```{r}
dash_and_hurdles_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles,
                                   family = Gamma(link = "log"))
```

We need the baseline model for our analysis as well
```{r}
dash_and_hurdles_one_gamma_log <- glm(RxnTime ~ 1, data = dash_and_hurdles, 
                                    family = Gamma(link = "log"))
```

```{r}
sim_two_effect_time <- function(model, base, RxnTime) {
  simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    sd_Venue <- vc$sdcor[1]
    sd_Venue_heat <- vc$sdcor[2]

    z1 <- rnorm(n, sd = sd_Venue)
    z2 <- rnorm(n, sd = sd_Venue_heat)

    shape <- 1 / sigma(model)^2
    mu <- exp(fixef(model) + z1 + z2)

  sbase <- summary(base)
  x <- simfit(model)
  print(mean(x < RxnTime))
  #print(quantile(x, prob = c(0.00001, 0.0001, 0.0005, 0.001)))
  ## compare with and without random effect
  #plot(density(x))  # with random effects
  #curve(dgamma(x, shape = 1 / sbase$dispersion, 
   #            scale = exp(coef(base)) * sbase$dispersion), 
  #      0.08, 0.25, add = TRUE, col = "blue")  # fixed effect only
}
```

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_two_effect_gamma_log, dash_and_hurdles_one_gamma_log, 0.1)
```
Now lets see how our results change when we include disqualifications
```{r}
dash_and_hurdles_with_dq <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  mutate(RxnTime = ifelse(RxnTime < 0, 0.000001, RxnTime))
```

```{r}
cat("The number of entries of the men's 100 meter dash and 110 meter hurdles
    without disqualifcations is", nrow(dash_and_hurdles_with_dq))
```

```{r}
dash_and_hurdles_with_dq_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles_with_dq,
                                   family = Gamma(link = "log"))
```

We need the baseline model for our analysis as well
```{r}
dash_and_hurdles_with_dq_one_gamma_log <- glm(RxnTime ~ 1, data = dash_and_hurdles_with_dq, 
                                    family = Gamma(link = "log"))
```

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_with_dq_two_effect_gamma_log, dash_and_hurdles_with_dq_one_gamma_log, 0.1)
```
## Lets repeat the previous section but exclude 2022 from our results
```{r}
dash_and_hurdles_no2022 <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS" & Time != "DQ" & Time != "D") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(Venue != 2022)
```

```{r}
dash_and_hurdles_no2022_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles_no2022,
                                   family = Gamma(link = "log"))

dash_and_hurdles_no2022_one_gamma_log <- glm(RxnTime ~ 1, data = dash_and_hurdles_no2022, 
                                    family = Gamma(link = "log"))
```

```{r}
set.seed(1)
sim_two_effect_time(dash_and_hurdles_no2022_two_effect_gamma_log, dash_and_hurdles_no2022_one_gamma_log, 0.1)
```

Now we analyze without 2022 but with disqualifications
```{r}
dash_and_hurdles_no2022_with_dq <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(RxnTime != 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles") |>
  filter(Venue != 2022) |>
  mutate(RxnTime = ifelse(RxnTime < 0, 0.000001, RxnTime))
```

```{r}
dash_and_hurdles_no2022_with_dq_two_effect_gamma_log <- glmer(RxnTime ~ (1 | Venue) +
                                                   (1 | Heat), 
                                   data = dash_and_hurdles_no2022_with_dq,
                                   family = Gamma(link = "log"))

dash_and_hurdles_no2022_with_dq_one_gamma_log <- glm(RxnTime ~ 1, data = dash_and_hurdles_no2022_with_dq, 
                                    family = Gamma(link = "log"))
```

```{r}
sim_two_effect_time(dash_and_hurdles_no2022_with_dq_two_effect_gamma_log, dash_and_hurdles_no2022_with_dq_one_gamma_log, 0.1)
```
